---
title: "Outcasts and Saboteurs: Analysis"
author: "Evan Carr, Andrew Reece"
output: html_document
---

## Setup
```{r load_pkgs, echo=FALSE, warning=FALSE}
library(pacman)
p_load(janitor, corrplot, pwr2, lmSupport, vcd, car, conflicted, glue, 
       Hmisc, mgcv, grid, psych, rlang, gridExtra, scales, emmeans, 
       magrittr, broom, boot, multcomp, ggthemr, stringr, 
       viridis, apaTables, cowplot, survival, survminer, ez, tidyverse)

conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("recode", "dplyr")
conflict_prefer("summarize", "dplyr")

source("helper_functions.R")
```

## Survey data  
This is a survey on belonging in the workplace. All participants from this survey 
were invited to participate in the subsequent Cyberball studies. This survey data 
is merged with data from the later experimental studies mainly for demographic 
information about participants. 
```{r study1_load_data, message=FALSE, warning=FALSE, echo=FALSE}
bel <- read_csv("data/belonging.csv")
```

Demographics
```{r study1_demog, message=FALSE, warning=FALSE}
get_demographics(bel)

glue("Total N = {nrow(bel)}")
glue("Mean age (SD) in years: {mean(bel$age) %>% round(2)} ({sd(bel$age) %>% round(2)})")
```

## Experimental study 1
```{r study1_load_data, message=FALSE, warning=FALSE, echo=FALSE}
study_1 <- read_csv("data/study_1.csv")
```

Demographics
```{r study1_demog, message=FALSE, warning=FALSE}
demog_study_1 <- demog_prep(study_1, bel)
full_demographics(demog_study_1)
summarise_demographics(demog_study_1)
```

Manipulation checks
```{r study1_manip}
study_1_manip_data <- study_1 %>% 
  select(condition, ignored, excluded, belonged, mc_percent_ball, starts_with("aas")) %>% 
  mutate(
    condition = case_when(
      condition == "Included" ~ 1,
      condition == "Excluded" ~ 0,
      TRUE ~ NA_real_),
    aas_pos = rowMeans(select(., aas_pos), na.rm = TRUE),
    aas_neg = rowMeans(select(., aas_neg), na.rm = TRUE))

manip_check_t(study_1_manip_data)
cohen.d(study_1_manip_data, "condition")$cohen.d
inspect_manip_vars(study_1)
ball_get_guess(study_1, condition)
create_manip_plot(study_1_manip_data, fill_colors = c("red", "blue"), aas = TRUE)
```

Analyze DVs
```{r study1_analyze}
max_tasks <- 110
get_2xN_cell_ct(study_1, condition, play_for)
study_1_fit_data <- binom_anova(study_1, max_tasks = max_tasks, prop = FALSE)
study_1_fit_data[["anova_summary"]]
study_1_contrasts <- get_contrasts(study_1_fit_data[["fit"]], NULL) %>% as_tibble()
```

Plot condition x play_for interaction
```{r study1_plot}
anno_df <- data.frame(expand(study_1, condition, play_for), 
                      anno_x = 1.5, anno_y = 22,
                      pval = c("p = .66", "p < .001"))

create_interaction_plot(study_1, anno_df, max_tasks)
```

## Study 2  
Update: Equalized expected value
```{r study2_load_data, message=FALSE, warning=FALSE, echo=FALSE}
study_2 <- read_csv("data/study_2.csv")
```

Get demographic data:
```{r study2_demog, message=FALSE, warning=FALSE}
demog_study_2 <- demog_prep(study_2, bel)
full_demographics(demog_study_2)
summarise_demographics(demog_study_2)
```

Analyze manipulation checks:
```{r study2_manip}
study_2_manip_data <- study_2 %>% 
  select(condition, ignored, excluded, belonged, mc_percent_ball, starts_with("aas")) %>% 
  mutate(
    condition = case_when(
      condition == "Included" ~ 1,
      condition == "Excluded" ~ 0,
      TRUE ~ NA_real_),
    aas_pos = rowMeans(select(., all_of(aas_pos)), na.rm = TRUE),
    aas_neg = rowMeans(select(., all_of(aas_neg)), na.rm = TRUE))

manip_check_t(study_2_manip_data)
cohen.d(study_2_manip_data, "condition")$cohen.d
inspect_manip_vars(study_2)
ball_get_guess(study_2, condition)

create_manip_plot(study_2_manip_data, fill_colors = c("red", "blue"), aas = TRUE)
```

Analyze main DVs:

```{r study2_analyze}
max_tasks_study_2 <- 100

get_2xN_cell_ct(study_2, condition, play_for)

study_2_fit_data <- binom_anova(study_2, max_tasks = max_tasks_study_2, prop = FALSE)
study_2_fit_data[["anova_summary"]]
study_2_contrasts <- get_contrasts(study_2_fit_data[["fit"]], NULL)
```

Plot main interaction:

```{r study2_plot}
anno_df <- data.frame(expand(study_2, condition, play_for), 
                      anno_x = 1.5, anno_y = 22.5,
                      pval = c("p = .51", "p < .001", "p = .51", "p < .001"))

create_interaction_plot(study_2, anno_df, max_tasks_study_2)
```

## Study 3  
Update: Add non-teammates "play for others" condition
```{r study3_load_data, message=FALSE, warning=FALSE, echo=FALSE}
study_3 <- read_csv("data/study_3.csv")
```

Demographics
```{r study3_demog}
demog_study_3 <- demog_prep(study_3, bel)
full_demographics(demog_study_3)
summarise_demographics(demog_study_3)
```

Manipulation checks
```{r study3_manip}
study_3_manip_data <- study_3 %>% 
  select(condition, ignored, excluded, belonged, mc_percent_ball, starts_with("aas")) %>% 
  mutate(
    condition = case_when(
      condition == "Included" ~ 1,
      condition == "Excluded" ~ 0,
      TRUE ~ NA_real_),
    aas_pos = rowMeans(select(., aas_pos), na.rm = TRUE),
    aas_neg = rowMeans(select(., aas_neg), na.rm = TRUE))

manip_check_t(study_3_manip_data)
cohen.d(study_3_manip_data, "condition")$cohen.d
inspect_manip_vars(study_3)
ball_get_guess(study_3, condition)

create_manip_plot(study_3_manip_data, fill_colors = c("red", "blue"), aas = TRUE)
```

Analyze DVs
```{r study3_analyze}
max_tasks_study_3 <- 15

get_2xN_cell_ct(study_3, condition, play_for)

study_3_fit_data <- binom_anova(study_3, max_tasks = max_tasks_study_3, prop = FALSE)
study_3_fit_data[["anova_summary"]]
study_3_contrasts <- get_contrasts(study_3_fit_data[["fit"]], c(1,10,15))
```

Plot interaction
```{r study3_plot}
anno_df <- data.frame(expand(study_3, condition, play_for), 
                      anno_x = 1.5, anno_y = 12.5,
                      pval = paste0("p ", c("= .20", "= .46", "< .001", 
                                            "= .20", "= .46", "< .001")))

create_interaction_plot(study_3, anno_df, max_tasks_study_3)
```

## Survival analysis (study_1 + study_2 + study_3)
```{r survival_setup}
cols <- c("workerId", "condition", "condition_int", "play_for", 
          "mc_percent_ball", "n_tasks", "prop_tasks", "missed_tasks")

datasets <- list(study_1, study_2, study_3) %>% 
  map(~select(.x, all_of(cols))) %>% 
  bind_rows(.id = "study_id") %>%
  mutate(max_tasks = n_tasks + missed_tasks,
         censor = if_else(missed_tasks == 0, 0, 1))
```

```{r survival_analyze}
# Self:
survobj_self <- Surv(time = filter(datasets, play_for == "Self") %>% pull(n_tasks), 
                     event = filter(datasets, play_for == "Self") %>% pull(censor))
survfit_self <- survfit(survobj_self ~ condition_int, data = filter(datasets, play_for == "Self"))
survdiff_self <- survdiff(survobj_self ~ condition_int, data = filter(datasets, play_for == "Self"))
coxph_self <- coxph(survobj_self ~ condition_int, data = filter(datasets, play_for == "Self"))
ggforest(coxph_self, data = filter(datasets, play_for == "Self"))

# Team:
survobj_team <- Surv(time = filter(datasets, play_for == "Team") %>% pull(n_tasks), 
                     event = filter(datasets, play_for == "Team") %>% pull(censor))
survfit_team <- survfit(survobj_team ~ condition_int, data = filter(datasets, play_for == "Team"))
survdiff_team <- survdiff(survobj_team ~ condition_int, data = filter(datasets, play_for == "Team"))
coxph_team <- coxph(survobj_team ~ condition_int, data = filter(datasets, play_for == "Team"))
ggforest(coxph_team, data = filter(datasets, play_for == "Team"))

# Check interaction using likelihood-ratio test to compare models:
survobj_both <- Surv(time = filter(datasets, play_for != "Charity") %>% 
                       pull(n_tasks), 
                     event = filter(datasets, play_for != "Charity") %>% 
                       pull(censor))

anova(
  coxph(survobj_both ~ condition_int + play_for, data = filter(datasets, play_for != "Charity")),
  coxph(survobj_both ~ condition_int * play_for, data = filter(datasets, play_for != "Charity"))
)
```

Survival plot
```{r survival_plot}
options(scipen = 6)
create_survplot(survfit_self, "A (Self)")
create_survplot(survfit_team, "B (Team)")
```

## Study 4  
Update: Add interventions
```{r study4_load_data, message=FALSE, warning=FALSE, echo=FALSE}
study_4 <- read_csv("data/study_4.csv")
```

Manipulation checks
```{r study4_manip}
study_4_manip_data <- study_4 %>% 
  select(condition, intervention, ignored, excluded, belonged, mc_percent_ball) %>%
  filter(condition == "Excluded") %>% 
  select(-condition) %>% 
  rename(condition = intervention)

# Only analyze within excluded condition:
study_4_cnd_excl <- filter(study_4, condition == "Excluded")
# Ignored:
anova_wrapper(data = study_4_cnd_excl, dv = ignored, interv = intervention)
# Excluded:
anova_wrapper(data = study_4_cnd_excl, dv = excluded, interv = intervention)
# Belonged:
anova_wrapper(data = study_4_cnd_excl, dv = belonged, interv = intervention)
# % Ball Tosses:
anova_wrapper(data = study_4_cnd_excl, dv = mc_percent_ball, interv = intervention)

inspect_manip_vars(study_4)
ball_get_guess(study_4, condition)

create_manip_plot(study_4_manip_data, aas = FALSE)

# Do same thing within included condition (to report in supplementary materials):
study_4_cnd_incl <- filter(study_4, condition == "Included")
# Ignored:
anova_wrapper(data = study_4_cnd_incl, dv = ignored, interv = intervention)
# Excluded:
anova_wrapper(data = study_4_cnd_incl, dv = excluded, interv = intervention)
# Belonged:
anova_wrapper(data = study_4_cnd_incl, dv = belonged, interv = intervention)
# % Ball Tosses:
anova_wrapper(data = study_4_cnd_incl, dv = mc_percent_ball, interv = intervention)

create_manip_plot(
  study_4 %>% 
    select(condition, intervention, ignored, excluded, belonged, mc_percent_ball) %>%
    filter(condition == "Included") %>% 
    select(-condition) %>% 
    rename(condition = intervention), 
  aas = FALSE
)
```

Analyze DVs
```{r study4_analyze}
get_2xN_cell_ct(study_4, condition, intervention)

# Get means & SDs for n_tasks by intervention:
study_4_summary <- study_4 %>% 
  group_by(condition, intervention) %>% 
  summarise(
    mean_tasks = mean(n_tasks, na.rm=T),
    sd_tasks = sd(n_tasks, na.rm=T),
    n = n()
  ) %>% 
  as.data.frame()

# Both included and excluded
study_4_fit_data_1 <- glm(cbind(n_tasks, missed_tasks) ~ condition*intervention, 
                       family=binomial(link="logit"),
                       data = study_4)
# Only excluded:
study_4_fit_data_2 <- glm(cbind(n_tasks, missed_tasks) ~ intervention, 
                       family=binomial(link="logit"),
                       data = filter(study_4, condition == "Excluded"))
study_4_fit_data_2 %>% Anova(., type = "II") %>% tidy()
study_4_emmeans <- study_4_fit_data_2 %>% emmeans(~intervention)
study_4_contrasts <- pairs(study_4_emmeans, adjust="holm")
study_4_contrasts

# Only included (for supplementary):
study_4_fit_data_3 <- glm(cbind(n_tasks, missed_tasks) ~ intervention, 
                       family=binomial(link="logit"),
                       data = filter(study_4, condition == "Included"))
study_4_fit_data_3 %>% Anova(., type = "II") %>% tidy()
study_4_fit_data_3 %>% emmeans(~intervention)
study_4_fit_data_3 %>% emmeans(~intervention) %>% pairs(adjust="holm")
```

Plot main findings
```{r study4_plot}
max_tasks_interventions <- 110

cnds <- c("Included", "Excluded")

summary_stats_team <- cnds %>% 
  map(~{datasets %>% 
      filter(condition == .x, play_for == "Team") %>% 
      group_split(study_id) %>% 
      map_dfr(~{summarise(
        .x,
        avg = pois_se(n_tasks)["y"],
        lo_se = pois_se(n_tasks)["ymin"],
        hi_se = pois_se(n_tasks)["ymax"],
        n = n())}, .id = "study_id")}) %>% 
  bind_rows(.id = "cnd_id")

# Only using study_2 for mean reference lines:
# Only within excluded condition:
study_4 %>% 
  filter(condition == "Excluded") %>% 
  ggplot(aes(x = intervention, y = n_tasks, fill = intervention)) + 
  stat_summary(fun.data = "pois_se", 
               fun.args = list(n = max_tasks_interventions, prop = FALSE),
               geom = "errorbar", color="black", width=.075, size=.75) +
  geom_hline(yintercept = 
               filter(study_2, condition == "Included", play_for == "Team") %>% 
                 pull(n_tasks) %>% 
                 mean(), 
             linetype="dashed", color="blue") +
  annotate("text", x = 1.2, y = 20.9, color = "blue", size = 3,
           label="Inclusion (team)\nmean in Study 2") +
  geom_hline(yintercept = 
               filter(study_2, condition == "Excluded", play_for == "Team") %>% 
                 pull(n_tasks) %>% 
                 mean(), 
             linetype="dashed", color="red") +
  annotate("text", x = 3.8, y = 15.75, color = "red", size = 3,
           label="Exclusion (team)\nmean in Study 2") +
  geom_point(stat = "summary", fun = "mean", shape = 21, color = "black", 
             size = 3, stroke = 1) +
  scale_fill_viridis_d() +
  labs(y = "Number of trials completed\nduring reward task",
       fill = "Intervention Type") +
  theme_bw() +
  theme(
    axis.title = element_text(size=11, face="bold"),
    axis.title.x = element_blank(),
    axis.text = element_text(size=10),
    axis.text.x = element_blank(),
    panel.grid = element_blank(),
    legend.text = element_text(size=9),
    legend.title = element_text(size=9, face="bold"),
    legend.position = "right",
    axis.ticks.x = element_blank()
  )

# Only within included condition (for supplementary materials):
study_4 %>% 
  filter(condition == "Included") %>% 
  ggplot(aes(x = intervention, y = n_tasks, fill = intervention)) + 
  stat_summary(fun.data = "pois_se", 
               fun.args = list(n = max_tasks_interventions, prop = FALSE),
               geom = "errorbar", color="black", width=.075, size=.75) +
  geom_hline(yintercept = 
               filter(study_2, condition == "Included", play_for == "Team") %>% 
                 pull(n_tasks) %>% 
                 mean(), 
             linetype="dashed", color="blue") +
  annotate("text", x = 1.2, y = 21.5, color = "blue", size = 3,
           label="Inclusion (team)\nmean in Study 2") +
  geom_hline(yintercept = 
               filter(study_2, condition == "Excluded", play_for == "Team") %>% 
                 pull(n_tasks) %>% 
                 mean(), 
             linetype="dashed", color="red") +
  annotate("text", x = 3.8, y = 15.75, color = "red", size = 3,
           label="Exclusion (team)\nmean in Study 2") +
  geom_point(stat = "summary", fun = "mean", shape = 21, color = "black", 
             size = 3, stroke = 1) +
  scale_fill_viridis_d() +
  labs(y = "Number of trials completed\nduring reward task",
       fill = "Intervention Type") +
  theme_bw() +
  theme(
    axis.title = element_text(size=11, face="bold"),
    axis.title.x = element_blank(),
    axis.text = element_text(size=10),
    axis.text.x = element_blank(),
    panel.grid = element_blank(),
    legend.text = element_text(size=9),
    legend.title = element_text(size=9, face="bold"),
    legend.position = "right",
    axis.ticks.x = element_blank()
  )
```


## Study 5  
Update: Replicate interventions  

Participants were screened via Qualtrics to meet the following criteria:  
  - Age > 18 years  
  - Income > $25k  
  - Currently employed  
  - Not self-employed  
  - Never played cyberball
```{r study5_load_data, message=FALSE, warning=FALSE, echo=FALSE}
study_5 <- read_csv("data/study_5.csv")
```

Demographics
```{r study5_demog}
demog_study_5 <- study_5 %>% 
  rename(
    sex = demog_gender,
    age = demog_age,
    race = demog_race,
    edu = demog_edu,
  )
full_demographics(demog_study_5)
summarise_demographics(demog_study_5)
```

Manipulation checks
```{r study5_manip}
study_5_manip_data <- study_5 %>% 
  select(workerId, cnd_intervention, ignored, excluded, 
         belonged, mc_percent_ball, aas_pos, aas_neg) %>% 
  rename(condition = cnd_intervention) %>% 
  mutate(condition = fct_relevel(condition, 
                                 "Exclusion (control)",
                                 "Inclusion (control)",
                                 "Perspective",
                                 "Mentorship",
                                 "Empowerment"),
         inclusion_code = if_else(condition == "Inclusion (control)", 1, 0))

inspect_manip_vars(study_5)
ball_get_guess(study_5, cnd_intervention)
create_manip_plot(study_5_manip_data, aas = TRUE)

# STATS with all 5 intervention conditions:
# Ignored:
anova_wrapper(data = study_5, dv = ignored, interv = condition)
# Excluded:
anova_wrapper(data = study_5, dv = excluded, interv = condition)
# Belonged:
anova_wrapper(data = study_5, dv = belonged, interv = condition)
# % Ball Tosses:
anova_wrapper(data = study_5, dv = mc_percent_ball, interv = condition)
# Positive Emotions:
anova_wrapper(data = study_5, dv = aas_pos, interv = condition)
# Negative Emotions:
anova_wrapper(data = study_5, dv = aas_neg, interv = cnd_intervention)

# STATS comparing inclusion control vs. all others (excluded):
# Ignored:
anova_wrapper(data = study_5_manip_data, dv = ignored, interv = inclusion_code)
# Excluded:
anova_wrapper(data = study_5_manip_data, dv = excluded, interv = inclusion_code)
# Belonged:
anova_wrapper(data = study_5_manip_data, dv = belonged, interv = inclusion_code)
# % Ball Tosses:
anova_wrapper(data = study_5_manip_data, dv = mc_percent_ball, interv = inclusion_code)
# Positive Emotions:
anova_wrapper(data = study_5_manip_data, dv = aas_pos, interv = inclusion_code)
# Negative Emotions:
anova_wrapper(data = study_5_manip_data, dv = aas_neg, interv = inclusion_code)

# STATS comparing between only exclusion conditions:
study_5_filtered <- filter(study_5, cnd_intervention != "Inclusion (control)")
# Ignored:
anova_wrapper(data = study_5_filtered, dv = ignored, interv = cnd_intervention)
# Excluded:
anova_wrapper(data = study_5_filtered, dv = excluded, interv = cnd_intervention)
# Belonged:
anova_wrapper(data = study_5_filtered, dv = belonged, interv = cnd_intervention)
# % Ball Tosses:
anova_wrapper(data = study_5_filtered, dv = mc_percent_ball, interv = cnd_intervention)
# Positive Emotions:
anova_wrapper(data = study_5_filtered, dv = aas_pos, interv = cnd_intervention)
# Negative Emotions:
anova_wrapper(data = study_5_filtered, dv = aas_neg, interv = cnd_intervention)
```

Analyze DVs
```{r study5_analyze}
# Get n_tasks summary data by condition:
study_5_summary <- study_5 %>% 
  group_by(cnd_intervention) %>% 
  summarize(
    mean_tasks = mean(n_tasks, na.rm=T),
    sd_tasks = sd(n_tasks, na.rm=T),
    n = n()
  ) %>% 
  as.data.frame()

# Fit model:
study_5_fit_data <- glm(cbind(n_tasks, missed_tasks) ~ cnd_intervention,
                          family = binomial(link="logit"),
                          data = study_5)
study_5_fit_data %>% Anova(., type = "II") %>% tidy()
study_5_emmeans <- study_5_fit_data %>% emmeans(~cnd_intervention)
study_5_contrasts <- pairs(study_5_emmeans, adjust="holm")
study_5_contrasts
```

Plot  findings
```{r study5_plot}
max_tasks_interventionsrep <- 110

study_5 %>% 
  ggplot(aes(x=fct_relevel(cnd_intervention, 
                           "Exclusion (control)",
                           "Inclusion (control)",
                           "Perspective",
                           "Mentorship",
                           "Empowerment"),
             y=n_tasks, 
             fill=fct_relevel(cnd_intervention, 
                              "Exclusion (control)",
                              "Inclusion (control)",
                              "Perspective",
                              "Mentorship",
                              "Empowerment"))) + 
  stat_summary(fun.data = "pois_se", 
               fun.args = list(n = max_tasks_interventionsrep, prop = FALSE),
               geom = "errorbar", color = "black", width = .075, size = .75) +
  geom_point(stat = "summary", fun = "mean", shape = 21, color = "black", 
             size = 3, stroke = 1) +
  labs(y = "Number of trials completed\nduring reward task",
       fill = "Condition") +
  scale_fill_viridis_d() +
  theme_bw() +
  theme(
    axis.title = element_text(size=11, face="bold"),
    axis.title.x = element_blank(),
    axis.text = element_text(size=10),
    axis.text.x = element_blank(),
    panel.grid = element_blank(),
    legend.text = element_text(size=9),
    legend.title = element_text(size=9, face="bold"),
    legend.position = "right",
    axis.ticks.x = element_blank()
  )
```

